Carbonate chemistry at Ny-Ålesund

### 2023-03-02 awipev-CO2.Rmd
update varianle names in Pangaea, some tweeks in figures

**Results are shown below but it does not make sense to udse them in the manuscript. Btter to use all pCO2-AT data as above.**

@@

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_sf, temp_fb, pco2_fb_insi_temp, pHint_tot_sf, at, ct, ph_s_sf_temp_insi) %>%
  dplyr::rename(`pressure [dbar]` = depth,          # hydrostatic pressure (profiler)
                `s_insitu [unit]` = sal_insitu_ctd, # salinity in situ (profiler)
                `s_fb [unit]` = sal_fb,             # salinity (FerryBox)
                `t_11m [°C]` = temp_insitu_11m,     # temperature in situ (static at 11 m)
                `t_ctd [°C]` = temp_insitu_ctd,     # temperature in situ (profiler)
                `t_fb [°C]` = temp_fb,              # temperature (FerryBox)
                `t_sf [°C]` = temp_sf,              # temperature SeaFET (profiler)
                `at [umol kg-1]` = at,              # total alkalinity in situ, discrete measurements
                #`at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
                `ct [umol kg-1]` = ct,              # dissolved inorganic carbon in situ, discrete measurements
                `ph_discrete [total scale]` = ph_s_sf_temp_insi, # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
                #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
                `pco2 [uatm]` = pco2_fb_insi_temp,  # Partial pressure of CO2 (FerryBox)
                #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
                `pH_sensor [total scale]` = pHint_tot_sf, # pH in situ at in situ temperature (profiler)
                #`pH_dur [total scale]` = pH_dur,
                #`pH_calc [total scale]` = ph_calc_fb
                ) %>% 
  dplyr::mutate(across(starts_with("pressure"), ~ round(.x, digits = 2)),
                across(starts_with("s_"), ~ round(.x, digits = 2)),
                across(starts_with("t_"), ~ round(.x, digits = 2)),
                across(starts_with("ph"), ~ round(.x, digits = 3)),
                across(starts_with("at") | 
                         starts_with("ct") |
                         starts_with("pco2"), ~ round(.x, digits = 1)),
                )
# replace NaNs by NAs
pangaea <- pangaea %>% 
  mutate_all(~ifelse(is.nan(.), NA, .))

@@

```{r, echo = FALSE, message = FALSE, warning = FALSE}
p_pco2_fb_remos <- d_all %>% 
  dplyr::select(depth, monthd, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
  dplyr::filter(depth < 4) %>% 
  dplyr::filter(if_all(everything(), is.finite)) %>% 
  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
  geom_point(col="blue", size = 1) +
  xlim(250, 400) + ylim(250, 400) +
  labs(title = "pCO2 at ctd temperature",
       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 11) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
#p_pco2_fb_remos
ggsave(filename = "figures/pco2_fb_remos.png", plot = p_pco2_fb_remos, width = 25, height = 25, units = "cm")

# Same thing but monthly median; code different because one wants to calculate delta
tmp <- d_all %>% 
  dplyr::select(depth, montht, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
  dplyr::filter(depth < 4) %>% 
  drop_na() %>% 
  dplyr::group_by(montht) %>% 
  dplyr::summarise(
    pco2_fb_ctd_temp = median(pco2_fb_ctd_temp, na.rm = TRUE),
    pco2_remos_ctd_temp = median(pco2_remos_ctd_temp, na.rm = TRUE), 
    delta_pco2_fb_remos_monthly = pco2_remos_ctd_temp - pco2_fb_ctd_temp
  )
p_pco2_fb_remos_month <- tmp %>% 
  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = montht)) +
  geom_point(col="blue", size = 5) +
  xlim(270, 355) + ylim(270, 355) +
  labs(title = "pCO2 at ctd temperature",
       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 15, height = 15, units = "cm")
ggsave(filename = "figures/essd/pco2_fb_remos_month.pdf", plot = p_pco2_fb_remos_month, width = 15, height = 15, units = "cm")

@@

ts_oa <- tmp %>%
  ggplot(aes(x = datetime, y = OmegaAragonite), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  ylim(0, 3) +
  labs(title="Aragonite saturation state (11 m)",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
  Mytheme(size_labs = size_labs)
ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
ggsave(filename = "figures/essd/OmegaAragonite.pdf", plot = ts_oa, width = 15, height = 10, units = "cm")

>>>>

**Results are shown below but it does not make sense to use them in the manuscript. Btter to use all pCO2-AT data as above.**

@@

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_sf, temp_fb, pco2_fb_insi_temp, pHint_tot_sf, at, ct, ph_s_sf_temp_insi) %>%
  dplyr::rename(
    `pressure_profiler [dbar]` = depth,
    # hydrostatic pressure
    `salinity_PSS78_profiler [unit]` = sal_insitu_ctd,
    # salinity in situ
    `salinity_PSS78_ferrybox [unit]` = sal_fb,
    # salinity (FerryBox)
    `temperature_ITS90_11m [°C]` = temp_insitu_11m,
    # temperature in situ (static at 11 m)
    `temperature_ITS90_profiler [°C]` = temp_insitu_ctd,
    # temperature in situ (profiler)
    `temperature_ITS90_ferrybox [°C]` = temp_fb,
    # temperature (FerryBox)
    `temperature_ITS90_seafet_profiler [°C]` = temp_sf,
    # temperature SeaFET (profiler)
    `ta_discrete [umol kg-1]` = at,
    # total alkalinity in situ, discrete measurements
    #`at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
    `dic_discrete [umol kg-1]` = ct,
    # dissolved inorganic carbon in situ, discrete measurements
    `ph_insitu_temperature_discrete [total scale]` = ph_s_sf_temp_insi,
    # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
    #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
    `pco2_insitu_temperature_ferrybox [uatm]` = pco2_fb_insi_temp,
    # partial pressure of CO2 at in situ temperature (FerryBox)
    #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
    `ph_insitu_temperature_profiler [total scale]` = pHint_tot_sf,
    # pH in situ at in situ temperature (profiler)
    #`pH_dur [total scale]` = pH_dur,
    #`pH_calc [total scale]` = ph_calc_fb
  ) %>% 
  dplyr::mutate(
    across(starts_with("pressure"), ~ round(.x, digits = 2)),
    across(starts_with("salinity"), ~ round(.x, digits = 2)),
    across(starts_with("temperature"), ~ round(.x, digits = 2)),
    across(starts_with("ph"), ~ round(.x, digits = 3)),
    across(
      starts_with("ta") |
        starts_with("dic") |
        starts_with("pco2"),
      ~ round(.x, digits = 1)
    ),
  )
# replace NaNs by NAs
pangaea <- pangaea %>% 
  mutate_all(~ifelse(is.nan(.), NA, .))

@@

```{r, echo = FALSE, message = FALSE, warning = FALSE}
p_pco2_fb_remos <- d_all %>% 
  dplyr::select(depth, monthd, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
  dplyr::filter(depth < 4) %>% 
  dplyr::filter(if_all(everything(), is.finite)) %>% 
  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
  geom_point(col="blue", size = 1) +
  xlim(250, 400) + ylim(250, 400) +
  #labs(title = "pCO2 at ctd temperature",
  labs(title = NULL,
       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 11) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
#p_pco2_fb_remos
ggsave(filename = "figures/pco2_fb_remos.png", plot = p_pco2_fb_remos, width = 25, height = 25, units = "cm")

# Same thing but monthly median; code different because one wants to calculate delta
tmp <- d_all %>% 
  dplyr::select(depth, montht, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
  dplyr::filter(depth < 4) %>% 
  drop_na() %>% 
  dplyr::group_by(montht) %>% 
  dplyr::summarise(
    pco2_fb_ctd_temp = median(pco2_fb_ctd_temp, na.rm = TRUE),
    pco2_remos_ctd_temp = median(pco2_remos_ctd_temp, na.rm = TRUE), 
    delta_pco2_fb_remos_monthly = pco2_remos_ctd_temp - pco2_fb_ctd_temp
  )
p_pco2_fb_remos_month <- tmp %>% 
  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = montht)) +
  geom_point(col="blue", size = 5) +
  xlim(270, 355) + ylim(270, 355) +
  #labs(title = "pCO2 at ctd temperature",
  labs(title = NULL,
       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 15, height = 15, units = "cm")
ggsave(filename = "figures/essd/pco2_fb_remos_month.pdf", plot = p_pco2_fb_remos_month, width = 15, height = 15, units = "cm")

@@

ts_oa <- tmp %>%
  ggplot(aes(x = datetime, y = OmegaAragonite), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  ylim(0, 3) +
  labs(title="",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
  Mytheme(size_labs = size_labs)
ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
ggsave(filename = "figures/essd/OmegaAragonite.pdf", plot = ts_oa, width = 15, height = 10, units = "cm")
